01_Vegetation_cover

### 2022-12-28 Manuscript.Rmd
start results

### Pollen representation by the vegetation
- missing species in pollen 
- 
### Effect of spatial scale and plant functional group
Over all treatments and spatial scales, we only found evidence of a significant positive relationship between pollen-based reconstructed CWM trait values and vegetation CWM values for plant height. We found little support for a positive association between pollen and vegetation trait value for leaf area and specific leaf area. The spatial scale matters for the relationship between pollen plant height and vegetation plant height, only at scales between 10-100 m the relationship is significant.

>>>>

### Pollen representation by the vegetation
- missing species in pollen 
- spatial scale

### Treatments
Over all treatments and spatial scales, we only found evidence of a significant positive relationship between pollen-based reconstructed CWM trait values and vegetation CWM values for plant height. We found little support for a positive association between pollen and vegetation trait value for leaf area and specific leaf area. The spatial scale matters for the relationship between pollen plant height and vegetation plant height, only at scales between 10-100 m the relationship is significant.
